### 2024-11-15 paper/nature-scientific-data-response-letter/response.tex

\AR Thank you for your remarks and questions. We have added detailed descriptions on the meaning of data files, their structure, properties and units, and their file size. Please also see our \hyperref[ac:datarecords]{previous response} (page \pageref{ac:datarecords}). With regard to your question, we need to clarify on what we originally meant in the manuscript. Using the examples of 380 kV and 400 kV voltage levels. Both voltage levels are commonly used for operating transmission grid assets, e.g. 400 kV in Denmark \cite{akhmatovNovelHarmonicDistortion2023} and 380 kV in Germany \cite{bnetzaBestaetigungNetzentwicklungsplanStrom2024} (\href{https://www.entsoe.eu/data/map}{https://www.entsoe.eu/data/map}). When we map pandapower's \cite{thurnerPandapowerOpenSourcePython2018} and PyPSA's \cite{brownPyPSAPythonPower2018} standard linetypes toe the respective lines, we use the closest voltage level available in the dataset. In the case of 380 kV and 400 kV, both are mapped to the `Al/St 240/40 4-bundle 380.0' line type \cite{brownPyPSAPythonPower2018}. Hence, they inherit the same underlying electrical parameters, such as resistance and impedance per km, as well as susceptance and nominal current. However, as they are operated at different voltage levels, as calculating the nominal apparent power includes the multiplication with the voltage level, the nominal apparent power is different for the two voltage levels. The line type column including all electric parameters are now also included in the updated dataset on Zenodo, so this should be more clear now.\cite{xiongPrebuiltElectricityNetwork2024}. We have also made this more clear in the revised manuscript to avoid any confusion.

\bibliography{references.bib}
